Open-source tools in R for landscape ecology

### 2021-01-20 paper/paper.Rmd
improves glossary

API & Application programming interface \\
cell & Smallest, rectangular unit of raster data model \\
CRAN & Comprehensive R Archive Network \\
CRS & Coordinate references systems \\
GIS & Geographical information system \\
landscapes & Mosaics of land covers, ecosystems, habitat types, land uses \\
NLM & Neutral landscape model \\
open-source software & Software released under licenses that allow to use, modify and distribute it \\
patch & Neighboring cells with same value \\
raster & Cell grid based data model \\
resolution & Size in meter or degree of one cell \\
R packages & User-created software extension to R programming language \\
SDM & Species distribution modelling \\
vector & Points and lines based data model \\

>>>>

API & Application programming interface \\
cell & Smallest, rectangular unit of raster data model \\
CRAN & Comprehensive R Archive Network \\
CRS & Coordinate references systems \\
GIS & Geographical information system \\
landscape & A mosaic of land covers, ecosystems, habitat types, land uses \\
NLM & Neutral landscape model \\
open-source software & Software released under licenses that allow to use, modify and distribute it \\
patch & Neighboring cells with same value \\
raster & Cell grid based data model \\
resolution & Size in meter or degree of one cell \\
R package & User-created software extension to R programming language \\
SDM & Species distribution modeling \\
vector & Points, lines, and polygons-based data model \\
